---
title: "MAF Analysis - TCGA-KIRC"
subtitle: "Laterality, Sex, and Smoking History Analysis"
output: html_document
---

# ============================================
# Setup and Load Libraries
# ============================================
```{r setup, message=FALSE, warning=FALSE}
if (!require("knitr", quietly = TRUE))
  install.packages("knitr")
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
if (!require("TCGAbiolinks", quietly = TRUE))
  BiocManager::install("TCGAbiolinks")
if (!require("maftools", quietly = TRUE))
  BiocManager::install("maftools")

library(BiocManager)
library(TCGAbiolinks)
library(maftools)

# Set output directory
output_dir <- "/home1/seunggeo/490_cluster/qbio490_fa25_final_KIRC/outputs"
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
```

# ============================================
# IMPORTANT NOTES FOR YOUR ANALYSIS
# ============================================

**Your Hypothesis:** Tumor laterality is associated with distinct genomic features 
that contribute to differences in overall survival. Laterality effects may differ 
across smoking history and sex.

**Key Variables to Analyze:**
1. **Laterality** - Left vs Right kidney
2. **Sex** - Male vs Female  
3. **Smoking History** - Never vs Ever smokers

**Why NOT to use TTN and MUC16:**
- TTN (Titin) and MUC16 (Mucin 16) are among the largest genes in the human genome
- They accumulate passenger mutations simply due to their size, not because they drive cancer
- They are NOT biologically meaningful in ccRCC analysis
- Key ccRCC driver genes are: **VHL, PBRM1, SETD2, BAP1, KDM5C, PTEN, MTOR**

# ============================================
# Step 1: Verify Clinical Variables
# ============================================
```{r check_variables}
# Check what clinical variables are available
cat("=== AVAILABLE CLINICAL VARIABLES ===\n\n")

# Check laterality
cat("1. LATERALITY:\n")
print(table(maf_object@clinical.data$laterality, useNA = "ifany"))

# Check gender
cat("\n2. GENDER:\n")
print(table(maf_object@clinical.data$gender, useNA = "ifany"))

# Check smoking - look for tobacco-related columns
cat("\n3. SMOKING-RELATED COLUMNS:\n")
smoking_cols <- grep("smok|tobacco", colnames(maf_object@clinical.data), 
                     ignore.case = TRUE, value = TRUE)
print(smoking_cols)

# If tobacco_smoking_history exists, show values
if ("tobacco_smoking_history" %in% colnames(maf_object@clinical.data)) {
  cat("\nTobacco smoking history values:\n")
  print(table(maf_object@clinical.data$tobacco_smoking_history, useNA = "ifany"))
}
```

# ============================================
# Step 2: Clean Clinical Variables
# ============================================
```{r clean_variables}
# Create cleaned versions of key variables

# --- Clean Laterality ---
maf_object@clinical.data$laterality_clean <- maf_object@clinical.data$laterality
maf_object@clinical.data$laterality_clean[
  maf_object@clinical.data$laterality_clean %in% c("", "[Not Available]", "[Discrepancy]")
] <- NA

cat("Laterality (cleaned):\n")
print(table(maf_object@clinical.data$laterality_clean, useNA = "ifany"))

# --- Clean Gender ---
maf_object@clinical.data$gender_clean <- maf_object@clinical.data$gender
maf_object@clinical.data$gender_clean[
  maf_object@clinical.data$gender_clean %in% c("", "[Not Available]")
] <- NA

cat("\nGender (cleaned):\n")
print(table(maf_object@clinical.data$gender_clean, useNA = "ifany"))

# --- Create Smoking Status (simplified: Never vs Ever) ---
# TCGA codes: 1=Lifelong Non-smoker, 2=Current smoker, 
# 3=Reformed >15yr, 4=Reformed ≤15yr, 5=Current reformed
if ("tobacco_smoking_history" %in% colnames(maf_object@clinical.data)) {
  maf_object@clinical.data$smoking_status <- NA
  maf_object@clinical.data$smoking_status[
    maf_object@clinical.data$tobacco_smoking_history == "1"
  ] <- "Never"
  maf_object@clinical.data$smoking_status[
    maf_object@clinical.data$tobacco_smoking_history %in% c("2", "3", "4", "5")
  ] <- "Ever"
  
  cat("\nSmoking Status (Never vs Ever):\n")
  print(table(maf_object@clinical.data$smoking_status, useNA = "ifany"))
}
```

# ============================================
# Step 3: Define Genes to Analyze
# ============================================
```{r define_genes}
# Passenger genes to EXCLUDE (large genes with random mutations)
passenger_genes <- c("TTN", "MUC16", "OBSCN", "CSMD3", "RYR2", "USH2A", 
                     "DNAH5", "SYNE1", "LRP1B", "ZFHX4", "PCLO")

# Known ccRCC DRIVER genes (biologically meaningful)
ccRCC_drivers <- c("VHL", "PBRM1", "SETD2", "BAP1", "KDM5C", "PTEN", "MTOR", 
                   "TP53", "PIK3CA", "ATM", "ARID1A", "SMARCA4")

# Get gene summary and filter out passengers
gene_summary <- getGeneSummary(maf_object)
gene_summary_filtered <- gene_summary[!Hugo_Symbol %in% passenger_genes]

# Show top mutated genes (excluding passengers)
cat("=== TOP 20 MUTATED GENES (excluding passengers) ===\n")
print(head(gene_summary_filtered[, .(Hugo_Symbol, MutatedSamples, AlteredSamples)], 20))

# Show ccRCC driver frequencies
cat("\n=== ccRCC DRIVER GENE FREQUENCIES ===\n")
driver_summary <- gene_summary[Hugo_Symbol %in% ccRCC_drivers]
print(driver_summary[order(-MutatedSamples), .(Hugo_Symbol, MutatedSamples)])

# Define top genes for plots (use filtered list)
top_genes <- head(gene_summary_filtered$Hugo_Symbol, 15)
cat("\n=== GENES TO USE IN ANALYSIS ===\n")
print(top_genes)
```

# ============================================
# Step 4: LATERALITY ANALYSIS (Primary Variable)
# ============================================
```{r laterality_analysis}
cat("=== LATERALITY ANALYSIS ===\n\n")

# Create subsets for Left vs Right
left_mask <- maf_object@clinical.data$laterality_clean == "Left"
left_mask[is.na(left_mask)] <- FALSE
left_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[left_mask]
left_maf <- subsetMaf(maf = maf_object, tsb = left_barcode)

right_mask <- maf_object@clinical.data$laterality_clean == "Right"
right_mask[is.na(right_mask)] <- FALSE
right_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[right_mask]
right_maf <- subsetMaf(maf = maf_object, tsb = right_barcode)

cat(paste0("Left kidney tumors: N = ", length(left_barcode), "\n"))
cat(paste0("Right kidney tumors: N = ", length(right_barcode), "\n"))
```

```{r laterality_coOncoplot, fig.width=14, fig.height=10}
# Co-Oncoplot: Left vs Right Kidney
coOncoplot(
  m1 = left_maf,
  m2 = right_maf,
  m1Name = paste0("Left Kidney (N=", length(left_barcode), ")"),
  m2Name = paste0("Right Kidney (N=", length(right_barcode), ")"),
  genes = top_genes,
  removeNonMutated = TRUE
)

# Save the plot
pdf(file.path(output_dir, "coOncoplot_laterality.pdf"), width = 14, height = 10)
coOncoplot(
  m1 = left_maf,
  m2 = right_maf,
  m1Name = paste0("Left Kidney (N=", length(left_barcode), ")"),
  m2Name = paste0("Right Kidney (N=", length(right_barcode), ")"),
  genes = top_genes,
  removeNonMutated = TRUE
)
dev.off()
cat("Saved: coOncoplot_laterality.pdf\n")
```

```{r laterality_comparison}
# Statistical comparison of mutation frequencies
laterality_comparison <- mafCompare(
  m1 = left_maf, 
  m2 = right_maf,
  m1Name = "Left",
  m2Name = "Right",
  minMut = 5
)

cat("\n=== STATISTICAL COMPARISON: Left vs Right ===\n")
print(head(laterality_comparison$results, 15))

# Save results
write.csv(laterality_comparison$results, 
          file.path(output_dir, "laterality_mutation_comparison.csv"),
          row.names = FALSE)
```

```{r laterality_forestplot, fig.width=10, fig.height=8}
# Forest plot showing odds ratios
forestPlot(mafCompareRes = laterality_comparison, 
           pVal = 0.1,
           geneFontSize = 0.8)

pdf(file.path(output_dir, "forestplot_laterality.pdf"), width = 10, height = 8)
forestPlot(mafCompareRes = laterality_comparison, pVal = 0.1, geneFontSize = 0.8)
dev.off()
cat("Saved: forestplot_laterality.pdf\n")
```

# ============================================
# Step 5: SEX/GENDER ANALYSIS
# ============================================
```{r sex_analysis}
cat("=== SEX/GENDER ANALYSIS ===\n\n")

# Create subsets for Male vs Female
male_mask <- maf_object@clinical.data$gender_clean == "MALE"
male_mask[is.na(male_mask)] <- FALSE
male_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[male_mask]
male_maf <- subsetMaf(maf = maf_object, tsb = male_barcode)

female_mask <- maf_object@clinical.data$gender_clean == "FEMALE"
female_mask[is.na(female_mask)] <- FALSE
female_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[female_mask]
female_maf <- subsetMaf(maf = maf_object, tsb = female_barcode)

cat(paste0("Male patients: N = ", length(male_barcode), "\n"))
cat(paste0("Female patients: N = ", length(female_barcode), "\n"))
```

```{r sex_coOncoplot, fig.width=14, fig.height=10}
# Co-Oncoplot: Male vs Female
coOncoplot(
  m1 = male_maf,
  m2 = female_maf,
  m1Name = paste0("Male (N=", length(male_barcode), ")"),
  m2Name = paste0("Female (N=", length(female_barcode), ")"),
  genes = top_genes,
  removeNonMutated = TRUE
)

pdf(file.path(output_dir, "coOncoplot_sex.pdf"), width = 14, height = 10)
coOncoplot(
  m1 = male_maf,
  m2 = female_maf,
  m1Name = paste0("Male (N=", length(male_barcode), ")"),
  m2Name = paste0("Female (N=", length(female_barcode), ")"),
  genes = top_genes,
  removeNonMutated = TRUE
)
dev.off()
cat("Saved: coOncoplot_sex.pdf\n")
```

```{r sex_comparison}
# Statistical comparison
sex_comparison <- mafCompare(
  m1 = male_maf, 
  m2 = female_maf,
  m1Name = "Male",
  m2Name = "Female",
  minMut = 5
)

cat("\n=== STATISTICAL COMPARISON: Male vs Female ===\n")
print(head(sex_comparison$results, 15))

write.csv(sex_comparison$results, 
          file.path(output_dir, "sex_mutation_comparison.csv"),
          row.names = FALSE)
```

```{r sex_forestplot, fig.width=10, fig.height=8}
forestPlot(mafCompareRes = sex_comparison, pVal = 0.1, geneFontSize = 0.8)

pdf(file.path(output_dir, "forestplot_sex.pdf"), width = 10, height = 8)
forestPlot(mafCompareRes = sex_comparison, pVal = 0.1, geneFontSize = 0.8)
dev.off()
cat("Saved: forestplot_sex.pdf\n")
```

# ============================================
# Step 6: SMOKING STATUS ANALYSIS
# ============================================
```{r smoking_analysis}
cat("=== SMOKING STATUS ANALYSIS ===\n\n")

if ("smoking_status" %in% colnames(maf_object@clinical.data)) {
  
  # Create subsets for Never vs Ever smokers
  never_mask <- maf_object@clinical.data$smoking_status == "Never"
  never_mask[is.na(never_mask)] <- FALSE
  never_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[never_mask]
  never_maf <- subsetMaf(maf = maf_object, tsb = never_barcode)
  
  ever_mask <- maf_object@clinical.data$smoking_status == "Ever"
  ever_mask[is.na(ever_mask)] <- FALSE
  ever_barcode <- maf_object@clinical.data$Tumor_Sample_Barcode[ever_mask]
  ever_maf <- subsetMaf(maf = maf_object, tsb = ever_barcode)
  
  cat(paste0("Never smokers: N = ", length(never_barcode), "\n"))
  cat(paste0("Ever smokers: N = ", length(ever_barcode), "\n"))
  
} else {
  cat("WARNING: smoking_status column not found. Check variable names.\n")
}
```

```{r smoking_coOncoplot, fig.width=14, fig.height=10}
if (exists("never_maf") && exists("ever_maf") && 
    length(never_barcode) > 10 && length(ever_barcode) > 10) {
  
  coOncoplot(
    m1 = never_maf,
    m2 = ever_maf,
    m1Name = paste0("Never Smokers (N=", length(never_barcode), ")"),
    m2Name = paste0("Ever Smokers (N=", length(ever_barcode), ")"),
    genes = top_genes,
    removeNonMutated = TRUE
  )
  
  pdf(file.path(output_dir, "coOncoplot_smoking.pdf"), width = 14, height = 10)
  coOncoplot(
    m1 = never_maf,
    m2 = ever_maf,
    m1Name = paste0("Never Smokers (N=", length(never_barcode), ")"),
    m2Name = paste0("Ever Smokers (N=", length(ever_barcode), ")"),
    genes = top_genes,
    removeNonMutated = TRUE
  )
  dev.off()
  cat("Saved: coOncoplot_smoking.pdf\n")
}
```

```{r smoking_comparison}
if (exists("never_maf") && exists("ever_maf") && 
    length(never_barcode) > 10 && length(ever_barcode) > 10) {
  
  smoking_comparison <- mafCompare(
    m1 = never_maf, 
    m2 = ever_maf,
    m1Name = "Never",
    m2Name = "Ever",
    minMut = 5
  )
  
  cat("\n=== STATISTICAL COMPARISON: Never vs Ever Smokers ===\n")
  print(head(smoking_comparison$results, 15))
  
  write.csv(smoking_comparison$results, 
            file.path(output_dir, "smoking_mutation_comparison.csv"),
            row.names = FALSE)
}
```

# ============================================
# Step 7: Fisher's Exact Test for Key Gene (VHL)
# ============================================

**Why VHL instead of TTN?**
- VHL (Von Hippel-Lindau) is THE key driver gene in ccRCC
- VHL mutations occur in ~50% of ccRCC cases
- VHL regulates HIF pathway, which controls angiogenesis
- TTN is a passenger gene with no biological relevance to ccRCC

```{r fisher_test_vhl}
# Use VHL - the most important driver gene in ccRCC
gene <- "VHL"

cat(paste0("=== FISHER'S EXACT TEST: ", gene, " vs Laterality ===\n\n"))

# Get samples with VHL mutations in each group
mut_left <- unique(subsetMaf(left_maf, genes = gene)@data$Tumor_Sample_Barcode)
mut_right <- unique(subsetMaf(right_maf, genes = gene)@data$Tumor_Sample_Barcode)

# Total samples in each group
n_left <- length(unique(left_maf@clinical.data$Tumor_Sample_Barcode))
n_right <- length(unique(right_maf@clinical.data$Tumor_Sample_Barcode))

# Create contingency table
# Rows: Mutation status (Mutated, Wild-type)
# Columns: Laterality (Left, Right)
contingency_table <- matrix(
  c(
    length(mut_left),           # Left + Mutated
    n_left - length(mut_left),  # Left + Wild-type
    length(mut_right),          # Right + Mutated
    n_right - length(mut_right) # Right + Wild-type
  ),
  nrow = 2,
  byrow = TRUE,
  dimnames = list(
    c("Mutated", "Wild-type"),
    c("Left", "Right")
  )
)

cat("Contingency Table:\n")
print(contingency_table)

# Fisher's Exact Test
fisher_result <- fisher.test(contingency_table)
cat("\nFisher's Exact Test Results:\n")
print(fisher_result)

cat("\n--- INTERPRETATION ---\n")
cat(paste0("P-value: ", round(fisher_result$p.value, 4), "\n"))
cat(paste0("Odds Ratio: ", round(fisher_result$estimate, 3), "\n"))

if (fisher_result$p.value < 0.05) {
  cat("Result: STATISTICALLY SIGNIFICANT (p < 0.05)\n")
  cat("There IS a significant association between VHL mutations and tumor laterality.\n")
} else {
  cat("Result: NOT statistically significant (p >= 0.05)\n")
  cat("There is NO significant association between VHL mutations and tumor laterality.\n")
}

if (fisher_result$estimate > 1) {
  cat("Odds ratio > 1: VHL mutations are MORE common in Left kidney tumors.\n")
} else if (fisher_result$estimate < 1) {
  cat("Odds ratio < 1: VHL mutations are LESS common in Left kidney tumors.\n")
} else {
  cat("Odds ratio = 1: VHL mutations are equally common in both groups.\n")
}
```

```{r mosaic_vhl, fig.width=8, fig.height=6}
# Mosaic plot for VHL
mosaicplot(
  contingency_table,
  main = paste(gene, "Mutation vs. Tumor Laterality"),
  color = c("#E74C3C", "#3498DB"),
  xlab = "Mutation Status",
  ylab = "Laterality"
)

pdf(file.path(output_dir, paste0("mosaic_", gene, "_laterality.pdf")), width = 8, height = 6)
mosaicplot(
  contingency_table,
  main = paste(gene, "Mutation vs. Tumor Laterality"),
  color = c("#E74C3C", "#3498DB"),
  xlab = "Mutation Status",
  ylab = "Laterality"
)
dev.off()
cat(paste0("Saved: mosaic_", gene, "_laterality.pdf\n"))
```

# ============================================
# Step 8: Lollipop Plots for Key Driver Genes
# ============================================
```{r lollipop_vhl, fig.width=12, fig.height=8}
# Lollipop plot comparing VHL mutations by laterality
lollipopPlot2(
  m1 = left_maf, 
  m2 = right_maf, 
  gene = "VHL",
  m1_name = "Left Kidney",
  m2_name = "Right Kidney"
)

pdf(file.path(output_dir, "lollipop_VHL_laterality.pdf"), width = 12, height = 8)
lollipopPlot2(m1 = left_maf, m2 = right_maf, gene = "VHL",
              m1_name = "Left Kidney", m2_name = "Right Kidney")
dev.off()
cat("Saved: lollipop_VHL_laterality.pdf\n")
```

```{r lollipop_pbrm1, fig.width=12, fig.height=8}
# PBRM1 - second most commonly mutated gene in ccRCC
lollipopPlot2(
  m1 = left_maf, 
  m2 = right_maf, 
  gene = "PBRM1",
  m1_name = "Left Kidney",
  m2_name = "Right Kidney"
)

pdf(file.path(output_dir, "lollipop_PBRM1_laterality.pdf"), width = 12, height = 8)
lollipopPlot2(m1 = left_maf, m2 = right_maf, gene = "PBRM1",
              m1_name = "Left Kidney", m2_name = "Right Kidney")
dev.off()
cat("Saved: lollipop_PBRM1_laterality.pdf\n")
```

```{r lollipop_setd2, fig.width=12, fig.height=8}
# SETD2 - another key ccRCC driver
tryCatch({
  lollipopPlot2(
    m1 = left_maf, 
    m2 = right_maf, 
    gene = "SETD2",
    m1_name = "Left Kidney",
    m2_name = "Right Kidney"
  )
  
  pdf(file.path(output_dir, "lollipop_SETD2_laterality.pdf"), width = 12, height = 8)
  lollipopPlot2(m1 = left_maf, m2 = right_maf, gene = "SETD2",
                m1_name = "Left Kidney", m2_name = "Right Kidney")
  dev.off()
  cat("Saved: lollipop_SETD2_laterality.pdf\n")
}, error = function(e) {
  cat("Note: SETD2 lollipop plot could not be generated (possibly low mutation count)\n")
})
```

# ============================================
# Step 9: Comprehensive Oncoplot with Clinical Annotations
# ============================================
```{r oncoplot_annotated, fig.width=16, fig.height=12}
# Create oncoplot with laterality, sex, and smoking annotations
clinical_features <- c("laterality_clean", "gender_clean")
if ("smoking_status" %in% colnames(maf_object@clinical.data)) {
  clinical_features <- c(clinical_features, "smoking_status")
}

oncoplot(
  maf = maf_object,
  genes = top_genes,
  clinicalFeatures = clinical_features,
  sortByAnnotation = TRUE,
  annotationFontSize = 0.8,
  fontSize = 0.6,
  drawRowBar = TRUE,
  drawColBar = TRUE
)

pdf(file.path(output_dir, "oncoplot_with_clinical.pdf"), width = 16, height = 12)
oncoplot(
  maf = maf_object,
  genes = top_genes,
  clinicalFeatures = clinical_features,
  sortByAnnotation = TRUE,
  annotationFontSize = 0.8,
  fontSize = 0.6,
  drawRowBar = TRUE,
  drawColBar = TRUE
)
dev.off()
cat("Saved: oncoplot_with_clinical.pdf\n")
```

# ============================================
# Step 10: Additional Fisher's Tests (Sex and Smoking)
# ============================================
```{r fisher_sex}
cat("=== FISHER'S EXACT TEST: VHL vs Sex ===\n\n")

mut_male <- unique(subsetMaf(male_maf, genes = "VHL")@data$Tumor_Sample_Barcode)
mut_female <- unique(subsetMaf(female_maf, genes = "VHL")@data$Tumor_Sample_Barcode)

n_male <- length(unique(male_maf@clinical.data$Tumor_Sample_Barcode))
n_female <- length(unique(female_maf@clinical.data$Tumor_Sample_Barcode))

sex_table <- matrix(
  c(
    length(mut_male), n_male - length(mut_male),
    length(mut_female), n_female - length(mut_female)
  ),
  nrow = 2, byrow = TRUE,
  dimnames = list(c("Mutated", "Wild-type"), c("Male", "Female"))
)

print(sex_table)
fisher_sex <- fisher.test(sex_table)
print(fisher_sex)

cat(paste0("\nP-value: ", round(fisher_sex$p.value, 4)))
cat(paste0("\nOdds Ratio: ", round(fisher_sex$estimate, 3), "\n"))
```

```{r fisher_smoking}
if (exists("never_maf") && exists("ever_maf")) {
  cat("\n=== FISHER'S EXACT TEST: VHL vs Smoking ===\n\n")
  
  mut_never <- unique(subsetMaf(never_maf, genes = "VHL")@data$Tumor_Sample_Barcode)
  mut_ever <- unique(subsetMaf(ever_maf, genes = "VHL")@data$Tumor_Sample_Barcode)
  
  n_never <- length(unique(never_maf@clinical.data$Tumor_Sample_Barcode))
  n_ever <- length(unique(ever_maf@clinical.data$Tumor_Sample_Barcode))
  
  smoking_table <- matrix(
    c(
      length(mut_never), n_never - length(mut_never),
      length(mut_ever), n_ever - length(mut_ever)
    ),
    nrow = 2, byrow = TRUE,
    dimnames = list(c("Mutated", "Wild-type"), c("Never", "Ever"))
  )
  
  print(smoking_table)
  fisher_smoking <- fisher.test(smoking_table)
  print(fisher_smoking)
  
  cat(paste0("\nP-value: ", round(fisher_smoking$p.value, 4)))
  cat(paste0("\nOdds Ratio: ", round(fisher_smoking$estimate, 3), "\n"))
}
```

# ============================================
# Summary
# ============================================
```{r summary}
cat("\n")
cat("========================================\n")
cat("        ANALYSIS COMPLETE              \n")
cat("========================================\n")
cat("\nFiles saved to:", output_dir, "\n")
cat("\nKey outputs generated:\n")
cat("  - coOncoplot_laterality.pdf\n")
cat("  - coOncoplot_sex.pdf\n")
cat("  - coOncoplot_smoking.pdf\n")
cat("  - forestplot_laterality.pdf\n")
cat("  - forestplot_sex.pdf\n")
cat("  - laterality_mutation_comparison.csv\n")
cat("  - sex_mutation_comparison.csv\n")
cat("  - smoking_mutation_comparison.csv\n")
cat("  - mosaic_VHL_laterality.pdf\n")
cat("  - lollipop_VHL_laterality.pdf\n")
cat("  - lollipop_PBRM1_laterality.pdf\n")
cat("  - oncoplot_with_clinical.pdf\n")
cat("\n")
cat("========================================\n")
cat("KEY CHANGES FROM ORIGINAL CODE:\n")
cat("========================================\n")
cat("1. Changed variable from 'history_of_malignancy' to LATERALITY\n")
cat("   (aligned with your hypothesis)\n")
cat("2. Excluded passenger genes (TTN, MUC16) - they are NOT drivers\n")
cat("3. Focus on ccRCC drivers: VHL, PBRM1, SETD2, BAP1\n")
cat("4. Added statistical comparisons with mafCompare()\n")
cat("5. Added forest plots showing odds ratios\n")
cat("6. Added stratified analyses (laterality + sex + smoking)\n")
cat("7. Proper Fisher's test on VHL (not TTN)\n")
cat("========================================\n")
```
